---
title: "R Notebook"
output: pdf_document
---

#Library
```{r}
library(dplyr)
library(tidyr)
library(tidyverse)
library(reshape2)
library(igraph)
library(networkD3) #Sankey
library(webshot) #html to png (sankey)
```

#Data

##Artifical 
for graphical abstract

```{r}
A <- matrix(c(0,1,0,0,0,1,0,1,0,0,1,1,0,1,0,0,0,0,0,1,0,0,0,1,0), nrow = 5, ncol = 5)
Ma <- matrix(c(0,1,1,0,0,1,0,0,0,0,0,0,0,0,1,0,0,1,0,0,0,0,1,1,0), nrow = 5, ncol = 5)

A
Ma
```

##Empirical

```{r}
dat_e <- read.csv2("edges_long.csv")
dat_n <- read.csv2("nodes.csv")
```

```{r}
dat_n$id <- as.character(dat_n$id)
```

```{r}
#wide edge list: layers are in columns
dat_e$l <- as.numeric(gsub("l", "", dat_e$layer))

dat_we <- dat_e %>% select(c("from","to","l")) %>% unique() %>% pivot_wider(names_from = "l", values_from = "l")
colnames(dat_we) <- c("from","to", paste0("l", c(3,1,4,2)))
dat_we[,3:ncol(dat_we)] <- replace(dat_we[,3:ncol(dat_we)], !is.na(dat_we[,3:ncol(dat_we)]), 1) #!is.na() to 1
dat_we <- dat_we %>% replace(is.na(.), 0) #is.na() to 0

dat_we$from <- as.character(dat_we$from)
dat_we$to <- as.character(dat_we$to)

dat_we <- dat_we[,c("from","to","l1","l2","l3","l4")]
```

#Q^pair l1, l2

observed network layer: l1 (cooperation)
null network layer: l2 (friendship)

##C_1: Configuration model as reference

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1
A <- as.matrix(as_adjacency_matrix(g, attr = "weight")) %>% replace(is.na(.), 0)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1)$community
                )
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_conf"
table(dat_n$c_l1_conf)
```

```{r}
#Q_c values
diag(louvain(A, gamma = 1)$B)/sum(A)

#Q^conf_l1
louvain(A, gamma = 1)$Q
```

```{r}
#modules by department
table(dat_n$dep, dat_n$c_l1_conf)
```

```{r}
dat_we <- left_join(dat_we, dat_n[,c("id","c_l1_conf")], by=c("from"="id"))
dat_we <- left_join(dat_we, dat_n[,c("id","c_l1_conf")], by=c("to"="id"))
```

```{r}
r <- data.frame()
for (i in 1:max(dat_n$c_l1_conf)){
  for (j in 1:max(dat_n$c_l1_conf)){
    x <- dat_we %>% filter(c_l1_conf.x==i & c_l1_conf.y==j & l1==1) %>% summarise_at(vars("l1":"l4"), mean)
    x$from <- i
    x$to <- j
    r <- rbind(r,x)
  }}
r

#the probability of l2, l3, l4 overlapping edges next to l1 edges in modules
r %>% filter(from == to)
```

##C_2: l1 paired l2 null network gamma = 1

```{r}
#A_ij observed network: l1
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1
A <- as.matrix(as_adjacency_matrix(g, attr = "weight")) %>% replace(is.na(.), 0)
```

```{r}
#P_ij null network: l2
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l2

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight")) %>% replace(is.na(.), 0)
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat=Ma)$community
                )
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_pair_g1"
table(dat_n$c_l1_l2_pair_g1)
```

```{r}
#Q_c values
diag(louvain(A, gamma = 1, mat = Ma)$B)/sum(A)

#Q^pair_l1l2
louvain(A, gamma = 1, mat = Ma)$Q
```

```{r}
#modules by department
table(dat_n$dep, dat_n$c_l1_l2_pair_g1)
```

```{r}
dat_we <- left_join(dat_we, dat_n[,c("id","c_l1_l2_pair_g1")], by=c("from"="id"))
dat_we <- left_join(dat_we, dat_n[,c("id","c_l1_l2_pair_g1")], by=c("to"="id"))
```

```{r}
r <- data.frame()
for (i in 1:max(dat_n$c_l1_l2_pair_g1)){
  for (j in 1:max(dat_n$c_l1_l2_pair_g1)){
    x <- dat_we %>% filter(c_l1_l2_pair_g1.x==i & c_l1_l2_pair_g1.y==j & l1==1) %>% summarise_at(vars("l1":"l4"), mean)
    x$from <- i
    x$to <- j
    r <- rbind(r,x)
  }}
r

#the probability of l2, l3, l4 overlapping edges next to l1 in modules
r %>% filter(from == to)
```


##C_3: l1 paired l2 null network gamma = 2

```{r}
#A_ij observed network: l1
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1
A <- as.matrix(as_adjacency_matrix(g, attr = "weight")) %>% replace(is.na(.), 0)
```

```{r}
#P_ij null network: l2
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l2

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight")) %>% replace(is.na(.), 0)
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 2, mat=Ma)$community
                )
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_pair_g2"
table(dat_n$c_l1_l2_pair_g2)
```

```{r}
#Q_c values
diag(louvain(A, gamma = 2, mat = Ma)$B)/sum(A)

#Q^pair_l1l2
louvain(A, gamma = 2, mat = Ma)$Q
```

```{r}
#modules by department
table(dat_n$dep, dat_n$c_l1_l2_pair_g2)
```

```{r}
dat_we <- left_join(dat_we, dat_n[,c("id","c_l1_l2_pair_g2")], by=c("from"="id"))
dat_we <- left_join(dat_we, dat_n[,c("id","c_l1_l2_pair_g2")], by=c("to"="id"))
```

```{r}
r <- data.frame()
for (i in 1:max(dat_n$c_l1_l2_pair_g2)){
  for (j in 1:max(dat_n$c_l1_l2_pair_g2)){
    x <- dat_we %>% filter(c_l1_l2_pair_g2.x==i & c_l1_l2_pair_g2.y==j & l1==1) %>% summarise_at(vars("l1":"l4"), mean)
    x$from <- i
    x$to <- j
    r <- rbind(r,x)
  }}
r

#the probability of l2, l3, l4 overlapping edges next to l1 in modules
r %>% filter(from == to)
```

##Sankey

```{r}
#the number of modules should rename because of simplify the figure

#links 1
x1 <- data.frame(source=dat_n$c_l1_conf, target=dat_n$c_l1_l2_pair_g1) %>% group_by(source, target) %>% summarise(value=n()) %>% as.data.frame()
x1$target <- x1$target+100
x1 <- x1 %>% filter(source<=6) #filter out modules from source with 1 member
x1$source <- dplyr::recode(x1$source, '1'=1, '2'=2, '3'=3, '4'=6, '5'=4, '6'=5) #rename modules to avoid crossing edges 
x1$target <- dplyr::recode(x1$target, '105'=101, '101'=102, '102'=103, '103'=104, '106'=105, '104'=106, '107'=107) #rename modules to avoid crossing edges 

#links 2
x2 <- data.frame(source=dat_n$c_l1_l2_pair_g1, target=dat_n$c_l1_l2_pair_g2) %>% group_by(source, target) %>% summarise(value=n()) %>% as.data.frame()
x2$source <- x2$source+100
x2$target <- x2$target+200
x2 <- x2 %>% filter(source<=107) #filter out modules from source with 1 member
x2$source <- dplyr::recode(x2$source, '105'=101, '101'=102, '102'=103, '103'=104, '106'=105, '104'=106, '107'=107) #rename modules to avoid crossing edges
x2$target <- dplyr::recode(x2$target, '211'=201, '203'=202, '201'=203, '202'=204, '204'=205, '205'=206, 
                           '206'=207, '212'=208, '215'=209, '216'=210, '207'=211, '210'=212, '208'=213, '214'=214,
                           '209'=215, '213'=216) #rename modules to avoid crossing edges

x <- rbind(x1,x2)

#nodes
y <- data.frame(name=c(as.character(x$source), as.character(x$target)) %>% unique())
y$groups <- as.factor(c(rep("a",6), rep("b",7), rep("c",15)))

#links to plot
x$IDsource <- match(x$source, y$name)-1 
x$IDtarget <- match(x$target, y$name)-1
x$groups <- as.factor(c("l"))

x$source <- factor(x$source, levels=unique(x$source))

my_color <- 'd3.scaleOrdinal() .domain(["a", "b","c","l"]) .range(["#b3e0ff","#b3ffb3","#ccffcc","#f3e5d8"])'

sn <- sankeyNetwork(Links = x, Nodes = y, Source = "IDsource", Target = "IDtarget", Value = "value", NodeID = "name",
              fontSize = 20, fontFamily = "Calibri", nodeWidth = 20, 
              colourScale=my_color, NodeGroup="groups", LinkGroup = "groups", iterations = 4,
              width = 400, height = 400)
sn
#saveNetwork(sn, "sn00.html")

#webshot("sn00.html", "sn00.png", vwidth = 400, vheight = 400, zoom=2)
```

#Q^compl l3, l4

##C_1: Configuration model as reference

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight")) %>% replace(is.na(.), 0)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1)$community
                )
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l3_conf"
table(dat_n$c_l3_conf)
```

```{r}
#Q_c values
diag(louvain(A, gamma = 1)$B)/sum(A)

#Q^conf_l1
louvain(A, gamma = 1)$Q
```

```{r}
#modules by department
table(dat_n$dep, dat_n$c_l3_conf)
```

```{r}
dat_we <- left_join(dat_we, dat_n[,c("id","c_l3_conf")], by=c("from"="id"))
dat_we <- left_join(dat_we, dat_n[,c("id","c_l3_conf")], by=c("to"="id"))
```

```{r}
r <- data.frame()
for (i in 1:max(dat_n$c_l3_conf)){
  for (j in 1:max(dat_n$c_l3_conf)){
    x <- dat_we %>% filter(c_l3_conf.x==i & c_l3_conf.y==j & l3==1) %>% summarise_at(vars("l1":"l4"), mean)
    x$from <- i
    x$to <- j
    r <- rbind(r,x)
  }}
r

#the probability of l1, l2, l4 overlapping edges next to l3 edges in modules
r %>% filter(from == to)
```

##C_2 l3 complement l4 gamma = 1

```{r}
#A_ij observed network: l3
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
#P_ij null network: l4
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l4

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-1)*-1 #generate complement graph of an unweighted network

Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A),
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- dplyr::left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l3_l4_compl_g1"
```

```{r}
#Q_c values of communities
diag(louvain(A, gamma = 1, mat = Ma)$B)/sum(A)

#Q^pair_l1l2
louvain(A, gamma = 1, mat = Ma)$Q

table(dat_n$c_l3_l4_compl_g1)
```

```{r}
dat_we <- left_join(dat_we, dat_n[,c("id","c_l3_l4_compl_g1")], by=c("from"="id"))
dat_we <- left_join(dat_we, dat_n[,c("id","c_l3_l4_compl_g1")], by=c("to"="id"))
```

```{r}
r <- data.frame()
for (i in 1:max(dat_n$c_l3_l4_compl_g1)){
  for (j in 1:max(dat_n$c_l3_l4_compl_g1)){
    x <- dat_we %>% filter(c_l3_l4_compl_g1.x==i & c_l3_l4_compl_g1.y==j & l3==1) %>% 
      summarise_at(vars("l1":"l4"), mean)
    x$from <- i
    x$to <- j
    r <- rbind(r,x)
  }}
r

#the probability of l1, l2, l4 overlapping edges next to l3 in communities
r %>% filter(from==to)
```

##C_2 l3 complement l4 gamma = 2

```{r}
#A_ij observed network: l3
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
#P_ij null network: l4
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l4

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-1)*-1 #generate complement graph of an unweighted network

Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A),
                c=louvain(A, gamma = 2, mat = Ma)$community)
dat_n <- dplyr::left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l3_l4_compl_g2"
```

```{r}
#Q_c values of communities
diag(louvain(A, gamma = 2, mat = Ma)$B)/sum(A)

#Q^pair_l1l2
louvain(A, gamma = 2, mat = Ma)$Q

table(dat_n$c_l3_l4_compl_g2)
```

```{r}
dat_we <- left_join(dat_we, dat_n[,c("id","c_l3_l4_compl_g2")], by=c("from"="id"))
dat_we <- left_join(dat_we, dat_n[,c("id","c_l3_l4_compl_g2")], by=c("to"="id"))
```

```{r}
r <- data.frame()
for (i in 1:max(dat_n$c_l3_l4_compl_g2)){
  for (j in 1:max(dat_n$c_l3_l4_compl_g2)){
    x <- dat_we %>% filter(c_l3_l4_compl_g2.x==i & c_l3_l4_compl_g2.y==j & l3==1) %>% 
      summarise_at(vars("l1":"l4"), mean)
    x$from <- i
    x$to <- j
    r <- rbind(r,x)
  }}
r

#the probability of l1, l2, l4 overlapping edges next to l3 in communities
r %>% filter(from==to)
```

##Sankey

```{r}
#links
x1 <- data.frame(source=dat_n$c_l3_conf, target=dat_n$c_l3_l4_compl_g1) %>% group_by(source, target) %>% summarise(value=n()) %>% as.data.frame()
x1$target <- x1$target+100
x1 <- x1 %>% filter(source<=6)
x1$source <- dplyr::recode(x1$source, '5'=1, '1'=2, '2'=3, '3'=4, '4'=5, '6'=6)
x1$target <- dplyr::recode(x1$target, '101'=101, '102'=102, '103'=103, '104'=104, '107'=105, '106'=106, '105'=107)

x2 <- data.frame(source=dat_n$c_l3_l4_compl_g1, target=dat_n$c_l3_l4_compl_g2) %>% group_by(source, target) %>% summarise(value=n()) %>% as.data.frame()
x2$source <- x2$source+100
x2$target <- x2$target+200
x2 <- x2 %>% filter(source<=107)
x2$source <- dplyr::recode(x2$source, '101'=101, '102'=102, '103'=103, '104'=104, '107'=105, '106'=106, '105'=107)
x2$target <- dplyr::recode(x2$target, '201'=201, '205'=202, '212'=203, '202'=204, '209'=205, '203'=206, 
                           '210'=207, '204'=208, '207'=209, '206'=210, '211'=211, '208'=212)

x <- rbind(x1,x2)

#nodes
y <- data.frame(name=c(as.character(x$source), as.character(x$target)) %>% unique())
y$groups <- as.factor(c(rep("a",6), rep("b",7), rep("c",12)))

#links to plot
x$IDsource <- match(x$source, y$name)-1 
x$IDtarget <- match(x$target, y$name)-1
x$groups <- as.factor(c("l"))

x$source <- factor(x$source, levels=unique(x$source))

my_color <- 'd3.scaleOrdinal() .domain(["a", "b","c","l"]) .range(["#b3e0ff","#b3ffb3","#ccffcc","#f3e5d8"])'

sn <- sankeyNetwork(Links = x, Nodes = y, Source = "IDsource", Target = "IDtarget", Value = "value", NodeID = "name",
              fontSize = 20, fontFamily = "Calibri", nodeWidth = 20, 
              colourScale=my_color, NodeGroup="groups", LinkGroup = "groups",
              width = 400, height = 400)
sn
saveNetwork(sn, "sn2.html")

webshot("sn2.html", "sn2.png", vwidth = 400, vheight = 400, zoom=2)
```

#Q^multi l1, l2, l3

##C_1: Configuration model of weighted

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_conf"
```

##C_2: l1, l2, l3 multi

###l1 null

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_multi_l1"
```

###l2 null

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l2

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_multi_l2"
```

###l3 null

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l3

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_multi_l3"
```

###l1_l2 null

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1 + dat_we$l2

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_multi_l1_l2"
```

###l1_l3 null

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1 + dat_we$l3

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_multi_l1_l3"
```

###l2_l3 null

```{r}
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3

A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
```

```{r}
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l2 + dat_we$l3

Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
```

```{r}
x <- data.frame(id=colnames(A), 
                c=louvain(A, gamma = 1, mat = Ma)$community)
dat_n <- left_join(dat_n, x, by="id")
colnames(dat_n)[colnames(dat_n)=="c"] <- "c_l1_l2_l3_multi_l2_l3"
```

##Compare

```{r}
compare(dat_n$c_l1_l2_l3_conf, dat_n$c_l1_l2_l3_multi_l1, method = "nmi")
compare(dat_n$c_l1_l2_l3_conf, dat_n$c_l1_l2_l3_multi_l2, method = "nmi")
compare(dat_n$c_l1_l2_l3_conf, dat_n$c_l1_l2_l3_multi_l3, method = "nmi")
compare(dat_n$c_l1_l2_l3_conf, dat_n$c_l1_l2_l3_multi_l1_l2, method = "nmi")
compare(dat_n$c_l1_l2_l3_conf, dat_n$c_l1_l2_l3_multi_l1_l3, method = "nmi")
compare(dat_n$c_l1_l2_l3_conf, dat_n$c_l1_l2_l3_multi_l2_l3, method = "nmi")
```

```{r}
#modularity
g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
louvain(A, gamma = 1)$Q

g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1
Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
louvain(A, gamma = 1, mat = Ma)$Q

g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1
Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
louvain(A, gamma = 1, mat = Ma)$Q

g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l3
Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
louvain(A, gamma = 1, mat = Ma)$Q

g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1 + dat_we$l2
Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
louvain(A, gamma = 1, mat = Ma)$Q

g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l1 + dat_we$l3
Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
louvain(A, gamma = 1, mat = Ma)$Q

g <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g)$weight <- dat_we$l1 + dat_we$l2 + dat_we$l3
A <- as.matrix(as_adjacency_matrix(g, attr = "weight"))
g1 <- graph_from_edgelist(as.matrix(dat_we[,c("from","to")]), directed = TRUE)
E(g1)$weight <- dat_we$l2 + dat_we$l3
Ma <- as.matrix(as_adjacency_matrix(g1, attr = "weight"))
Ma <- (Ma-max(Ma))*-1
Ma <- Ma/sum(Ma)*sum(A)
louvain(A, gamma = 1, mat = Ma)$Q
```

